Circular Regression Trees and Forests with an Application to Probabilistic Wind Direction Forecasting

### 2019-12-12 pkg/circtree/inst/wind_paper/draft/draft.Rnw
small corrections
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2928 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: cb5a7e31fea719a1eb8678bcbefde44289bd01d9

    tree is built with the newly developed R-package \pkg{circtree} employing the

@@

    constructed based on $100$~individual trees employing the R-package

>>>>

    tree is built with the newly developed \textsf{R} package \pkg{circtree} employing the

@@

    constructed based on $100$~individual trees employing the \textsf{R} package
